---
title: "Final Fruit Tree Pruning Project"
author: "Trenton Blais"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# ABSTRACT



# BACKGROUND



# STUDY QUESTION and HYPOTHESIS

## Questions  
Does pruning apple trees increase the likelihood of an adequate fruit yield.

## Hypothesis 
We hypothesize that due to the benefits pruning typically produces, the trees that were pruned will lead to more adequate yields compared to the non-pruned trees.
  
## Prediction
We predict that pruning apple trees will increase the likelihood of an adequate yield for those trees. 

# METHODS


## Fill in first analysis

```{r loading data}
Pruned <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,3,3,3,3)



Not  <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,3,3,3,3,3)

Tree <- data.frame(Pruned, Not)

boxplot(Tree)

```

## Fill in second analysis/plot
I will also do a linear regression model on Thursday to test the relationship between the fruit trees' pruned status and its growth.

# DISCUSSION


## Interpretation - 

## Interpretation - Linear model and p-value


# CONCLUSION


# REFERENCES     

3. ChatGPT. OpenAI, version Jan 2025. Used as a reference for functions such as plot(viremia) and to correct syntax errors. Accessed `r Sys.Date()`.